First Order Nonsmooth Optimization: Catalyst Acceleration and Unifying Nesterov's Acceleration

### 2025-01-28 Notebook LaTEX/Proposal/presentation.tex
>w<, small changes sync

@@

@@

            Discussion at the end of their is summarized here as: 
            \begin{block}{Future works}
                Extend our results for variance reduced incremental methods such as the Catalyst Framework. 

        \end{frame}
        \begin{frame}{Our questions on Catalyst Acceleration}
            \begin{block}{A key detail about Catalyst}
                The smoothness assumption is baked into Assumption \ref{ass:linear-convergence-inner-loop}, where it states that the $\mathbb M$ needs to have linear convergence rate. 
            \end{block}
            All VRMs method in the literature requires Lipschitz smoothness and strong convexity to achieve linear convergence rate. 
            No linear convergent first order algorithm exists for all strong convex function by Theorem 2.1.5 in Nesterov's book \cite{nesterov_lectures_2018}. 
            Hence, here is our question: 
            \begin{alertblock}{Our question}
                Solving inexact proximal point doesn't necessarily need smoothness assumption on $F$ so what if we Assumption \ref{ass:linear-convergence-inner-loop} is false? 
            \end{alertblock}
            Next slide we explain why the answer is not trivial and why it's interesting. 
        \end{frame}
        \begin{frame}{The answer to our question is nontrivial}
            Without smoothness assumption on $F$, the following considerations apply. 
            \begin{enumerate}
                \item $\mathbb A$ optimizes inexact Moreau Envelope $\mathcal M^*_{\kappa^{-1}, F}(y)$ which is smooth and strongly convex if $F$ is convex hence the $\mathcal O(1/\sqrt{k})$ lower bound of Theorem 3.2.1 \cite{nesterov_lectures_2018} complexity for all convex first order optimization doesn't apply for the total complexity.  
                \item Instead, Theorem 2.1.7 \cite{nesterov_lectures_2018} applies and the lower complexity bound $\mathbb A$ is $\mathcal O(1/k^2)$. 
                \item Linear convergence of $\mathbb M$ Theorem 2.1.17 fails instead Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
            \end{enumerate}
            We note that the question has practical importance because the method of subgradient descent with Polyak stepsizes are optimal for Smooth, strongly convex, and smooth plus strongly convex function on a compact domain. See Hazan and Kakade\cite{hazan_revisiting_2022}. 
        \end{frame}

>>>>

            \begin{block}{Catalyst notations}

@@

            They are examples of incremental methods. 

@@

            Discussion about Catalyst future works is summarized here: 
            \begin{alertblock}{Future works}
                Extend linear convergence of accelerated gradient for variance reduced incremental methods such as the Catalyst Framework into a weaker settings. 
            \end{alertblock}

        \end{frame}
        \begin{frame}{Our question on Catalyst Acceleration}
            \begin{block}{A key detail about Catalyst}
                The smoothness assumption is baked into Assumption \ref{ass:linear-convergence-inner-loop}, where it states that the $\mathbb M$ needs to have linear convergence rate. 
            \end{block}
            All VRMs method in the literature requires Lipschitz smoothness and strong convexity to achieve linear convergence rate. 
            No linear convergent first order algorithm exists for all strong convex function by Theorem 2.1.5 in Nesterov's book \cite{nesterov_lectures_2018}. 
            Hence, here is our question: 
            \begin{alertblock}{Our question}
                Solving inexact proximal point doesn't necessarily need smoothness assumption on $F$ so what if we Assumption \ref{ass:linear-convergence-inner-loop} is false? 
            \end{alertblock}
            Next slide we explain why the answer is not trivial and why it's interesting. 
        \end{frame}
        \begin{frame}{The answer to our question is nontrivial}
            Without smoothness assumption on $F$, the following considerations apply. 
            \begin{enumerate}
                \item $\mathbb A$ optimizes inexact Moreau Envelope $\mathcal M^*_{\kappa^{-1}, F}(y)$ which is smooth and strongly convex if $F$ is convex hence the $\mathcal O(1/\sqrt{k})$ lower bound of Theorem 3.2.1 \cite{nesterov_lectures_2018} complexity for all convex first order optimization doesn't apply for the total complexity.  
                \item Instead, Theorem 2.1.7 \cite{nesterov_lectures_2018} applies and the lower complexity bound $\mathbb A$ is $\mathcal O(1/k^2)$. 
                \item Linear convergence of $\mathbb M$ Theorem 2.1.17 fails instead Theorem 3.2.5 applies and the lower bound is $\mathcal O(1/k)$. 
            \end{enumerate}
            We note that the question has practical importance because the method of subgradient descent with Polyak stepsizes are optimal for Smooth, strongly convex, and smooth plus strongly convex function on a compact domain. See Hazan and Kakade\cite{hazan_revisiting_2022}. 
        \end{frame}
